### 2018-10-08 Sections/errors_in_quantum_networks.tex
minor

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{free_space_dispersion}
	\caption{Spot-size of an optical beam grows quadratically with distance from the source. If the beam is then collected via an aperture of area $A'$, any component of $A$ falling outside of $A'$ is effectively lost, yielding an effective loss channel with efficiency \mbox{$\eta = \frac{A'}{A} = \frac{A'}{\pi d^2 \tan^2\theta} = O\left(\frac{1}{d^2}\right)$}.} \label{fig:free_space_disp}
\end{figure}

>>>>

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{free_space_dispersion}
	\caption{Spot-size of an optical beam grows quadratically with distance from the source. If the beam is then collected via a camera with aperture area $A'$, any component of $A$ falling outside of $A'$ is effectively lost, yielding an effective loss channel with efficiency \mbox{$\eta = \frac{A'}{A} = \frac{A'}{\pi d^2 \tan^2\theta} = O\left(\frac{1}{d^2}\right)$}.} \label{fig:free_space_disp}
\end{figure}
